Tropical Andes IUCN Montane and Lowland forest

### 2024-05-14 code/L0/L0_TropicalAndes_IUCNhabitatClassification.Rmd
add figure path, missing packages, and package citation with session info

# Set file paths
```{r}
data_path <- file.path('G:/Shared drives/SpaCE_Lab_FRUGIVORIA/data/plants/L0')
output_path <- file.path('G:/Shared drives/SpaCE_Lab_FRUGIVORIA/data/plants/L0')
```

# Load required packages
```{r}
library(raster)
library(sf)
library(rnaturalearth)
library(dplyr)
library(terra)
```

@@

```{r}
MapPlot <-
ggplot() +
geom_sf(data = worldMap, fill = "white") +
geom_sf(data = ECpoly, fill = Andean_states) +
geom_sf(data = VEpoly, fill = Andean_states) +
geom_sf(data = COpoly, fill = Andean_states) +
geom_sf(data = PEpoly, fill = Andean_states) +
geom_sf(data = BOpoly, fill = Andean_states) +
geom_sf(data = TropicalAndes, fill = Tropical_Andes) +
geom_sf(data = Forest_sf, fill = Forest) +
labs(title = "Tropical Andes IUCN Montane and Lowland forest", x = "Latitude", y = "Longitude") +
coord_sf(xlim = c(-94, -54), ylim = c(-24, 14), expand = FALSE) +
annotation_scale(location = "bl", width_hint = 0.5) +
annotation_north_arrow(location = "bl", which_north = "true", 
  pad_x = unit(0.75, "in"), pad_y = unit(0.5, "in"), style = north_arrow_fancy_orienteering) +
theme(panel.background = element_rect(fill = "lightblue"))

@@

```{r}
ggsave(filename = "Tropical Andes Forest Map.png", dpi = 300, device="png")
```

>>>>

# Set file paths
```{r}
data_path <- file.path('G:/Shared drives/SpaCE_Lab_FRUGIVORIA/data/plants/L0')
output_path <- file.path('G:/Shared drives/SpaCE_Lab_FRUGIVORIA/data/plants/L0')
figure_path <- file.path('G:/Shared drives/SpaCE_Lab_FRUGIVORIA/data/plants/figures')
```

# Load required packages
```{r}
library(raster)
library(sf)
library(rnaturalearth)
library(dplyr)
library(terra)
library(ggplot2)
library(ggspatial)
```

@@

```{r}
MapPlot <-
ggplot() +
geom_sf(data = worldMap, fill = "white") +
geom_sf(data = ECpoly, fill = Andean_states) +
geom_sf(data = VEpoly, fill = Andean_states) +
geom_sf(data = COpoly, fill = Andean_states) +
geom_sf(data = PEpoly, fill = Andean_states) +
geom_sf(data = BOpoly, fill = Andean_states) +
geom_sf(data = TropicalAndes, fill = Tropical_Andes) +
geom_sf(data = Forest_sf, fill = Forest) +
labs(title = "Tropical Andes IUCN Montane and Lowland forest", x = "Latitude", y = "Longitude") +
coord_sf(xlim = c(-85, -60), ylim = c(-24, 14), expand = FALSE) +
annotation_scale(location = "bl", width_hint = 0.5) +
annotation_north_arrow(location = "bl", which_north = "true", 
  pad_x = unit(0.75, "in"), pad_y = unit(0.5, "in"), style = north_arrow_fancy_orienteering) +
theme(panel.background = element_rect(fill = "lightblue"))

@@

```{r}
ggsave(filename = "Tropical Andes Forest Map.png", dpi = 300, device="png", path = output_path)
```

# Cite packages and print session info
```{r}
library(report)
cite_packages()

devtools::session_info()
```
